A Large-scale Study of Polymorphism in R

### 2019-03-28 paper/main.tex
discussing possible function annotations

# possible annotations:
# [1] x: {double, list<double>} -> {double, list<double>}
# [2] x: {double -> double, x: list<double> -> list<double>}
\end{lstlisting}}\caption{Possible function annotations.}\label{fig:funanno}\end{figure}
The first annotation option is

>>>>

# possible annotations:
# [1] x: {double, list<double>} -> {double, list<double>}
# [2] x: {double -> double, x: list<double> -> list<double>}
\end{lstlisting}}\caption{Possible function annotations.}\label{fig:funanno}\end{figure}
\AT{Say more about this?}

Harkening back to our discussion of character/real polymorphism, we mentioned that we might want to consider such a type signature to be a list or vector index only if a list or vector was present as another argument.
Now, this may be moving well beyond the purview of R programmers, but perhaps there is value in such a scenario, particularly if we include even {\it more} information in a type system.
For example, say we have a function which takes in a 2D point list.
There are a plethora of useful annotations, here, and of varying degrees of granularity.
We might want simply a "list" annotation, or we might want a "list<double>" annotation to be more specific.
In addition, though, we might want to know if the list has a names attribute, yielding "list<double>@names".
Then, perhaps it would be useful to know what the names were, so "list<double>@names\{x, y\}".

Now, depending on the granularity of individual argument annotations, we might want to link certain arguments together.
Consider the code snippet in Figure~\ref{fig:indexof}
\begin{figure}[!hb]{\small\begin{lstlisting}[style=R]
access <- function(l, i) l[[i]]

L <- list(a=1, b=2, c=3)
access(L, 2) # => 2
access(L, "c") # => 3

# possible annotations:
# [1] l: list, i: {character, real} -> real
# [2] l: list<double>, i: {character, real} -> real
# [3] l: list<X>, i: {character, real} -> X
# [4] l: list<double>@names, i: index -> double
# [5] l: list<double>@names{a, b, c}, i: index@indexOf(l) -> double
\end{lstlisting}}\caption{Linking annotations.}\label{fig:indexof}\end{figure}
The annotations could be used to generate code to check for compliance, like a contract.
